04_DESeq_sexes

### 2019-05-30 analysis/04_DESeq2_sexes.Rmd
new legends and stuff

```{r plottotalDEGs, eval = T}
a <- plottotalDEGs(DEGs.female_hypothalamus, "female hypothalamus")
b <- plottotalDEGs(DEGs.female_pituitary, "female pituitary")
c <- plottotalDEGs(DEGs.female_gonad, "female gonad")
d <- plottotalDEGs(DEGs.male_hypothalamus, "male hypothalamus")
e <- plottotalDEGs(DEGs.male_pituitary, "male pituitary")
f <- plottotalDEGs(DEGs.male_gondad, "male gonad")

myDEGs <- plot_grid(a + theme_noaxislabels,
          d + theme_noaxislabels,
          b + theme_noaxislabels,
          e + theme_noaxislabels,
          c + theme_nolegend,
          f + theme_nolegend,
          nrow = 3) 
myDEGs

pdf("../figures/sexes/plottotalDEGs-1.pdf", width = 12, height = 10)
plot(myDEGs)
dev.off()
```

@@

```{r plotpca, eval=T}
p1 <- plotPCAs(pcas.female_hypothalamus, "female hypothalamus") 
p2 <- plotPCAs(pcas.female_pituitary, "female pituitary")   
p3 <- plotPCAs(pcas.female_gonad, "female gonad") 
p4 <- plotPCAs(pcas.male_hypothalamus, "male hypothalamus") 
p5 <- plotPCAs(pcas.male_pituitary, "male pituitary") 
p6 <- plotPCAs(pcas.male_gondad, "male gonad") 
p1 + theme_noaxislabels
p2 + theme_noaxislabels
p3 + theme_noaxislabels
p4 + theme_noaxislabels
p5 + theme_noaxislabels
p6 + theme_noaxislabels

```
```{r pca, eval = T}
mylegend <- get_legend(p1)

allPC1s <- plot_grid(p1 + theme_noaxislabels + ylim(c(-35,35)), 
                     p4 + theme_noaxislabels + ylim(c(-35,35)), 
                     p2 + theme_noaxislabels + ylim(c(-35,35)),
                     p5 + theme_noaxislabels + ylim(c(-35,35)),
                     p3 + theme_nolegend + ylim(c(-35,35)) ,
                     p6 + theme_nolegend + ylim(c(-35,35)) ,
                     ncol = 2)

@@

pdf("../figures/sexes/pca-1.pdf", width = 12, height = 10)
plot(pc1)
dev.off()
```

@@

>>>>

```{r plottotalDEGs, eval = T}
a <- plottotalDEGs(DEGs.female_hypothalamus, "female hypothalamus: hatch is most unique parental stage")
b <- plottotalDEGs(DEGs.female_pituitary, "female pituitary: hatch and day before are most unique")
c <- plottotalDEGs(DEGs.female_gonad, "female gonad: variable across all parental stages")
d <- plottotalDEGs(DEGs.male_hypothalamus, "male hypothalamus: many parental contrasts yield 0 DEGs")
e <- plottotalDEGs(DEGs.male_pituitary, "male pituitary: peaks at hatch")
f <- plottotalDEGs(DEGs.male_gondad, "male gonad: most parental contrasts yield 0 DEGs")

myDEGs <- plot_grid(a + theme_noaxislabels,
          d + theme_siggenes,
          b + theme_noaxislabels,
          e + theme_noaxislabels,
          c + theme_noaxislabels,
          f + theme_noaxislabels,
          nrow = 3) 
myDEGs

pdf("../figures/sexes/plottotalDEGs-1.pdf", width = 12, height = 10)
plot(myDEGs)
dev.off()

@@

```{r pca, eval=T}
p1 <- plotPC1(pcas.female_hypothalamus, "female hypothalamus", "26% PC1 variance explained") 
p2 <- plotPC1(pcas.female_pituitary, "female pituitary", "11% PC1 variance explained")   
p3 <- plotPC1(pcas.female_gonad, "female gonad", "37% PC1 variance explained") 
p4 <- plotPC1(pcas.male_hypothalamus, "male hypothalamus", "28% PC1 variance explained") 
p5 <- plotPC1(pcas.male_pituitary, "male pituitary" , "11% PC1 variance explained") 
p6 <- plotPC1(pcas.male_gondad, "male gonad", "14% PC1 variance explained")

mylegend <- get_legend(p1)

allPC1s <- plot_grid(p1 + theme_nolegend + ylim(c(-35,35)), 
                     p4 + theme_nolegend + ylim(c(-35,35)), 
                     p2 + theme_nolegend + ylim(c(-35,35)),
                     p5 + theme_nolegend + ylim(c(-35,35)),
                     p3 + theme_nolegend + ylim(c(-35,35)) ,
                     p6 + theme_nolegend + ylim(c(-35,35)) ,
                     ncol = 2)

@@

pdf("../figures/sexes/pca-1.pdf", width = 12, height = 14)
plot(pc1)
dev.off()

p11 <- plotPC2(pcas.female_hypothalamus, "female hypothalamus", "9% PC2 variance explained") 
p12 <- plotPC2(pcas.female_pituitary, "female pituitary", "8% PC2 variance explained")   
p13 <- plotPC2(pcas.female_gonad, "female gonad", "12 PC2 variance explained") 
p14 <- plotPC2(pcas.male_hypothalamus, "male hypothalamus", "9% PC2 variance explained") 
p15 <- plotPC2(pcas.male_pituitary, "male pituitary" , "9% PC2 variance explained") 
p16 <- plotPC2(pcas.male_gondad, "male gonad", "10% PC2 variance explained")

allPC2 <- plot_grid(p11 + theme_nolegend + ylim(c(-35,35)), 
                     p14 + theme_nolegend + ylim(c(-35,35)), 
                     p12 + theme_nolegend + ylim(c(-35,35)),
                     p15 + theme_nolegend + ylim(c(-35,35)),
                     p13 + theme_nolegend + ylim(c(-35,35)) ,
                     p16 + theme_nolegend + ylim(c(-35,35)) ,
                     ncol = 2)

pc2 <- plot_grid(allPC2, mylegend,  nrow = 2, rel_heights = c(1.0, 0.15))
pc2

pdf("../figures/sexes/pca-2.pdf", width = 12, height = 14)
plot(pc2)
dev.off()

@@

## new heat maps

```{r correlationheatmaps, eval = T}
colData.female_hypothalamus <- subsetcolData(a.colData,  "female_hypothalamus")
colData.female_pituitary <- subsetcolData(a.colData,  "female_pituitary" )
colData.female_gonad <- subsetcolData(a.colData,  "female_gonad" )
colData.male_hypothalamus <- subsetcolData(a.colData,  "male_hypothalamus" )
colData.male_pituitary <- subsetcolData(a.colData,  "male_pituitary"  )
colData.male_gondad <- subsetcolData(a.colData,  "male_gonad")

plotcorrelationheatmaps(dds.female_hypothalamus, colData.female_hypothalamus ,"female hypothalamus: hatch, nest bldg., lay and day-before-hatch cluster")
plotcorrelationheatmaps(dds.female_pituitary, colData.female_pituitary, "female pituitary: clustering suggests an internal clock effect")
plotcorrelationheatmaps(dds.female_gonad, colData.female_gonad,  "female gonad: highly correlated across incubation and early nestling care")
plotcorrelationheatmaps(dds.male_hypothalamus, colData.male_hypothalamus, "male hypothalamus: 100% correlated across most parental care stages")
plotcorrelationheatmaps(dds.male_pituitary, colData.male_pituitary, "male pituitary: non-parental males are most different")
plotcorrelationheatmaps(dds.male_gondad, colData.male_gondad, "male gonad: non-parental males are most different")
```
